---
title: "tibbletest"
output: github_document
---

[![Travis build status](https://travis-ci.org/MethodsConsultants/tibbletest.svg?branch=master)](https://travis-ci.org/MethodsConsultants/tibbletest)
[![Codecov test coverage](https://codecov.io/gh/MethodsConsultants/tibbletest/branch/master/graph/badge.svg)](https://codecov.io/gh/MethodsConsultants/tibbletest?branch=master)

## Installation

Install the development version from [GitHub](https://github.com/) with: 

```{r, eval = FALSE}
devtools::install_github("MethodsConsultants/tibbletest")
```

## Usage

#### `propensity_weighting`

```{r, error = TRUE}

library(tibbletest)

example_dat %>%
  add_propensity_weights(
    treatment = "treat",
    ivs = c("age", "sugar_factor", "gender")
  )

example_dat %>%
  tidyr::drop_na(treat, age) %>%
  add_propensity_weights(
    treatment = "treat",
    ivs = c("age", "sugar_factor", "gender")
  ) %>%
  dplyr::glimpse()

```

#### `preprocess`

The `preprocess()` function is used to clean variable names, add descriptive variable labels, and convert binary variables to logical variables for better presentation in a descriptives table.

```{r}

library(tibbletest)

# defaults
example_dat %>% 
  dplyr::rename(`sugar   factor` = sugar_factor) %>% 
  preprocess()

# non-defaults
mylabels <- list(
  gender           = "Sex",
  sugar_factor     = "Sugar Amount",
  treat2           = "Alternative Treatment"
)

example_dat %>% 
  dplyr::rename(`sugar   factor` = sugar_factor) %>% 
  preprocess(clean_names = TRUE, convert_to_logical = FALSE, var_labels = mylabels)

# suppress messages
example_dat %>% 
  dplyr::rename(`sugar   factor` = sugar_factor) %>% 
  preprocess(quiet = TRUE)
```


#### `descriptives`

The `descriptives()` function is used to quickly create descriptives tables for reports or presentations.

```{r, error = TRUE}

example_dat %>% 
  descriptives(
    treatment = "treat", 
    variables = c("age", "sugar_factor", "gender", "happiness", "happy")
  )

example_dat %>%
  dplyr::select(treat, age, gender) %>%
  descriptives(
    treatment = "treat"
  )

example_dat %>%
  dplyr::select(treat, weight, age, gender, sugar_factor) %>%
  add_propensity_weights(
    treatment = "treat",
    ivs = c("age", "sugar_factor", "gender")
  ) %>% 
  descriptives(
    treatment = "treat",
    weights = "weight"
  )

example_dat %>% 
  descriptives(
    treatment = "treat", 
    variables = c("age", "sugar_factor", "gender", "happiness", "happy"),
    nonparametric = c("age")
  )
```

#### `format_tbl`

```{r}

univariate <- example_dat %>% 
  descriptives(
    variables = c("age", "sugar_factor", "gender", "happiness", "happy")
  )

univariate

univariate %>%
  format_tbl()

bivariate <- example_dat %>% 
  descriptives(
    treatment = "treat",
    variables = c("age", "sugar_factor", "gender", "happiness", "happy")
  )

bivariate

bivariate %>%
  format_tbl()
```

